---
title: "Leaflet Mappery"
author: "Andrew M."
date: "8/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggmap)
library(leaflet)
library(dplyr)
```

## Haunts of Ernest Hemingway

Behold this map showing places where renowned author Ernest Hemingway
frequented -- a supremely useful demonstration of mapping in R.

By the way, today's date is **August 13, 2018**.

First, let's create a data frame with Hemingway data:

```{r message=F}
ehdata <- data.frame(
  city = c('Oak Park, IL', 'Paris, France', 'Pamplona, Spain', 'Madrid, Spain',
            'Havana, Cuba', 'Key West, Florida', 'Ketchum, ID'),
  detail = c('Born, 1899', 'Writing of course', 'Bullfights, 1920s',
             'Journalism, 1930s', 'Lived here 1940s-ish',
             'House with lots of cats, 1940s', 'Died, 1961, A Moveable Feast sadly unfinished')
)

# Get locations from ggmap's geocode
latlon <- geocode(as.character(ehdata$city)) %>% rename(lng = lon)
ehdata <- cbind(ehdata, latlon)

# Popup messages
popup <- paste(ehdata$city, '<br>', ehdata$detail)
```

Now, the map. Click for fascinating biographical details!

```{r message=F}
ehdata %>% leaflet %>% addTiles() %>% addMarkers(popup=popup)
```

***

**Sources:**

"Places Where Hemingway Lived or Traveled," The New York Times, October 2015.
https://www.nytimes.com/2015/10/04/travel/places-where-hemingway-lived-or-traveled.html

